\documentclass[11pt,]{article}
\usepackage[sc, osf]{mathpazo}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}




\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% Now begins the stuff that I added.
% ----------------------------------

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\large\bf}
\subsectionfont{\rmfamily\mdseries\normalsize\itshape}


% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}


% Make parskips rather than indent with lists.
\usepackage{parskip}
\usepackage{titlesec}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}

% Use fontawesome. Note: you'll need TeXLive 2015. Update.
\usepackage{fontawesome}

% Fancyhdr, as I tend to do with these personal documents.
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.0pt}
\lhead{}
\chead{}
\rhead{}
\lfoot{
\cfoot{\scriptsize  William M. Murrah - CV }}
\rfoot{\scriptsize \thepage/{\hypersetup{linkcolor=black}\pageref{LastPage}}}

% Always load hyperref last.
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref

\hypersetup{unicode=true,
            pdftitle={William M. Murrah:  CV (Curriculum Vitae)},
            pdfauthor={William M. Murrah},
            pdfkeywords={education, educational psychology},
            colorlinks=true,
            linkcolor=blue,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true, bookmarks=true}
\urlstyle{same}  % don't use monospace font for urls

\begin{document}


\centerline{\huge \bf William M. Murrah}

\vspace{2 mm}

\hrule

\vspace{2 mm}

\moveleft.5\hoffset\centerline{Assistant Professor, Educational Research, Measurement, and Analysis
Program}
\moveleft.5\hoffset\centerline{Auburn University, Auburn AL 36849}
\moveleft.5\hoffset\centerline{ \faEnvelopeO \hspace{1 mm} \href{mailto:}{\tt \href{mailto:wmm0017@auburn.edu}{\nolinkurl{wmm0017@auburn.edu}}} \hspace{1 mm}  \faPhone \hspace{1 mm}  334/844-3806  \hspace{1 mm}  \faGithub \hspace{1 mm} \href{http://github.com/wmmurrah}{\tt wmmurrah} \hspace{1 mm}    \faGlobe \hspace{1 mm} \href{http://statistical-thinking.com}{\tt statistical-thinking.com}    | \emph{Updated:} \today}

\vspace{2 mm}

\hrule


\hypertarget{education}{%
\section{Education}\label{education}}

\hypertarget{ph.d.-educational-psychology-university-of-virginia-2010.}{%
\subsection{Ph.D.~Educational Psychology, University of Virginia,
2010.}\label{ph.d.-educational-psychology-university-of-virginia-2010.}}

\begin{itemize}
\item
  Dissertation: Comparing self-regulatory and early academic skills as
  predictors of later math, reading, and science elementary school
  achievement.
\item
  Co-chairs: David W. Grissmer, Herbert C. Richards.
\end{itemize}

\hypertarget{m.ed.-community-and-agency-counseling-university-of-montevallo-1998.}{%
\subsection{M.Ed. Community and Agency Counseling, University of
Montevallo,
1998.}\label{m.ed.-community-and-agency-counseling-university-of-montevallo-1998.}}

\hypertarget{b.s.-psychology-university-of-montevallo-1993.}{%
\subsection{B.S. Psychology, University of Montevallo,
1993.}\label{b.s.-psychology-university-of-montevallo-1993.}}

\hypertarget{current-position}{%
\section{Current Position}\label{current-position}}

\begin{itemize}
\tightlist
\item
  \textbf{Assistant Professor}, \emph{Educational Research, Measurement,
  and Assessment Program, Educational Foundations, Leadership, \&
  Technology}, \textbf{Auburn University} , 2016-present.
\end{itemize}

\hypertarget{research}{%
\section{Research}\label{research}}

\hypertarget{publications}{%
\subsection{Publications}\label{publications}}

* indicates collaboration with students.

\textbf{Murrah, W M.} (2020) Compound Bias Due to Measurement Error When
Comparing Regression Coefficients. \emph{Educational and Psychological
Measurement} 80(3), 548-577.

Chesser, S. S, \textbf{Murrah, W. M.}, Forbes, S. A. (2020). Impact of
personality and choice of instructional media on students' performance
in online and face-to-face courses, \emph{Computers in Human Behavior}.

*Brinkerhoff, S. A.,\textbf{Murrah, W. M.}, Hutchison, Z., Miller, M.,
\& Roper, J. A. (2019) Words matter: Instructions dictate
``self-selected'' walking speed in young adults. \emph{Gait \& Posture}.

Frug'e, A.D., *Smith, K.S., Riviere, A.J., Demark-Wahnefried, W.,
Arthur, A.E., \textbf{Murrah, W.M.}, Morrow, C.D., Arnold, R.D. \&
Braxton-Lloyd, K. (2019). Primary outcomes of a randomized controlled
crossover trial to explore the effects of a high chlorophyll dietary
intervention to reduce colon cancer risk in adults: The Meat and Three
Greens (M3G) Feasibility Trial. \emph{Nutrients} 11(10), 2349.

*Friesen, K. B., Barfield, J. W., \textbf{Murrah, W. M.}, Dugas, J. R.,
Andrews, J. R., \& Oliver, G. D. (2019). The association of upper body
kinematics and ERA of National Collegiate Athletics Association Division
I softball pitchers. \emph{Journal of Strength and Conditioning
Research}.

Brock, L. L., \textbf{Murrah, W. M.}, Cottone, E. A., Mashburn, A. J.,
\& Grissmer, D. W. (2017). An after-school intervention targeting
executive function and visuospatial skills also improves classroom
behavior. \emph{International Journal of Behavioral Development}.

\textbf{Murrah, W. M.}, Kosovich, J. J., \& Hulleman, C. S. (2016).
Measuring Fidelity in Educational Settings. In Roberts, G., Vaughn, S.,
Beretvas, T., \& Wong, V. (Eds.), \emph{Implementation Fidelity in
Randomized Educational Trials: An Applied Perspective.} Routledge.

Cameron, C. E., Cottone, E. A., \textbf{Murrah, W. M.} \& Grissmer, D.
W. (2016). How are motor skills linked to children's school performance
and academic achievement? \emph{Child Development Perspectives, 10(2)},
93-98.

*Kim, H., Schmidt, K. M., \textbf{Murrah, W. M.}, Cameron, C. E., \&
Grissmer, D. (2015). A Rasch Analysis of the KeyMath-3 Diagnostic
Assessment. \emph{Journal of Applied Measurement}, 16(4), 365-378.

*Kim, H., \textbf{Murrah, W. M.}, Cameron, C. E., Brock, L. L., Cottone,
E. A., \& Grissmer, D. (2014). Psychomotor properties of the
Teacher-Reported Motor Skills Rating Scale. \emph{Journal of
Psychoeducational Assessment}, first published on October 6, 2014 as
\url{doi:10.1177/0734282914551536}.

Ponitz, C. C., Brock, L. L., \textbf{Murrah, W. M.}, Bell, L., Worzalla,
S., Grissmer, D. W., \& Morrison, F. J. (2012). Fine motor skills and
executive function both contribute to kindergarten achievement.
\emph{Child Development}, 83(4), 1229-1244.

Grissmer, D., Grimm, K.J., Aiyer, S.M., \textbf{Murrah, W. M.}, \&
Steele, J.S. (2010). Fine motor skills and early comprehension of the
world: Two new school readiness indicators. \emph{Developmental
Psychology}, 46(5), 1008-1017.

\hypertarget{publications-in-press}{%
\subsection{Publications in Press}\label{publications-in-press}}

* indicates collaboration with students.

*Wright, T. K., \textbf{Murrah, W. M.}, Zabala M. E. (in press). Knee
Valgus vs.~Knee Abduction Angle: Comparative Analysis of Medial Knee
Collapse Definitions in Female Athletes, \emph{Journal of Biomechanical
Engineering}.

\hypertarget{publications-in-preparation}{%
\subsection{Publications in
Preparation}\label{publications-in-preparation}}

* indicates collaboration with students.

\textbf{Murrah. W. M.}, Frances, M., Silverman, D., Hulleman, C. S. (in
preparation). Student trajectories through front-door math courses in
community college.

Hulleman, C. S., Tibbetts, Y., \textbf{Murrah, W. M.} (in preparation).
Impacts of a utility value intervention among community college students
in front-door math courses.

Hulleman, C. S., Lee, M.,\textbf{Murrah, W. M.} et al.~(in preparation).
From politics to hurricanes: Lessons learned from a research-practice
partnership focused on improving motivation in community college math.

\hypertarget{presentations}{%
\subsection{Presentations}\label{presentations}}

Francis, M., Tibbetts, Y., Murrah, W. M., Phelps, J., Silverman, D.,
Moran, M., Kosovich, J., \& Hulleman, C. (2018) \emph{Using a
utility-value intervention to remove barriers in gateway math courses.}
Poster presented at the 2018 Understanding Interventions Conference,
Baltimore, MD.

Murrah, W. M., Ruzek, E. A., \& Grissmer, D. W. (2017) \emph{Children's
fine motor skills are important for school readiness and science
achievement.} Symposium presented at the Society for Research in Child
Development 2017 Biennial Meeting, Austin, TX.

Murrah, W. M.(2015) \emph{The Relative Importance of School Readiness
Skills as Predictors of First, Third, and Eighth Grade Achievement}.
Poster presented at the Society for Research in Child Development
Biennial Meeting, Philadelphia, PA.

Murrah, W. M., Grissmer, D., Ko, Michelle, Player, D., Cabell, S.,
O'Brien, R. H.(2015). \emph{Early achievement impacts of Core Knowledge
charter schools on early comprehension and general knowledge through 1st
grade.} Presented at Association for Education Finance and Policy Annual
Conference. Washington, DC.

Murrah. W. M. (2013) \emph{The evolution and evaluation of a play-based,
after-school curriculum that improves executive function, visuospatial
and math skills for disadvantaged children.} Organizer of seminar and
presenter at the Society for Research on Educational Effectiveness Fall
Conference. Washington, DC.

Murrah. W. M. (2011). \emph{Explaining the association between fine
motor skills and math achievement.} Seminar presented to the faculty and
students of the developmental psychology department at the University of
Virginia. Charlottesville, VA

Murrah, W. M. (2011). \emph{Fine motor skills predict later math,
science, and reading achievement}. Symposium presented at the Society
for Research in Child Development 2011 Biennial Meeting, Montreal,
Quebec.

Murrah, W. M. (2010). \emph{Fine motor skills as a predictor of later
math, reading, and science elementary achievement.} Paper presented to
the Conference on Human Development, 2010 Annual Meeting, New York City,
NY.

Murrah, W. M. (2009). \emph{Which developmental skills predict later
math, reading, and science elementary school achievement?} Paper
presented to National Science Foundation Advisory Board, 2009.
Charlottesville, VA.

\hypertarget{grant-funding}{%
\section{Grant Funding}\label{grant-funding}}

\hypertarget{current-funding}{%
\subsection{Current Funding}\label{current-funding}}

Auburn University National Alumni Council Grant Educational Learning
Community Improvement. PI: Andrew Pendola. \$1,617. Grant to support
QMER Workshop development and implementation.

\hypertarget{pending-funding}{%
\subsection{Pending Funding}\label{pending-funding}}

Strategic Teams Engaging in Meaningful Learning \& Leadership (STEM-L2).
PI: Victoria Cardullo. \emph{National Science Foundation}. Approximately
1,500,000. Project Period 9/01/2021 - 8/31/2025. Role: Co-Investigator.

\hypertarget{previous-funding}{%
\subsection{Previous Funding}\label{previous-funding}}

Removing Barriers to Success in Mathematics: An Integrative
Expectancy-Value Intervention. PI: Chris Hulleman. \emph{National
Science Foundation}. Approximately \$1,500,000. Project Period:
9/01/2015 - 8/31/2019. Role: Senior Personnel/Methodologist.

Developmental Skills Linked to Math and Science Achievement: An
Interdisciplinary Data-Intensive Approach to Identification and
Improvement through Experimental Intervention. \emph{National Science
Foundation}. Approximately \$2,500,000. Project Period: 9/1/2013 -
8/31/2018. Role: Research Scientist/Methodologist.

Evaluation of Core Knowledge charter schools in Colorado.
\emph{Institute of Education Sciences}. Approximately \$4,900,000.
Project Period: 07/01/2009 - 12/31/2015. Role: Research
Scientist/Methodologist.

Efficacy of the WINGS after-school social and emotional learning (SEL)
program. \emph{Institute of Education Sciences}. Approximately
\$2,700,000. Project Period: 09/01/2011 - 8/31/2015. Role: Research
Scientist/Methodologist.

Math and science achievement gaps for minority and disadvantaged
students: Developmental and environmental influences from nine months to
8th grade, \emph{National Science Foundation}, 2008 - 2012 (\$952,710)
Role: Co-Investigator/Methodologist.

Improving fine motor skill development to promote mathematical ability,
\emph{Institute of Education Sciences}, 2009 - 2012 (\$462,765) Role:
Primary Data Analyst

New kindergarten readiness indicators for math and science: Next steps
in validation, communication and projecting policy impacts,
\emph{National Science Foundation}, 2010-2012 (\$297,653) Role:
Co-investigator/Methodologist.

\hypertarget{other-research-experience}{%
\subsection{Other Research Experience}\label{other-research-experience}}

Research Associate, \emph{University of Virginia}, Summer 2010--Spring
2014.

Graduate Research Assistant, \emph{University of Virginia}, Summer
2009--Spring 2010.

Curry Participant Pool Coordinator, \emph{University of Virginia},
Summer 2008- Spring 2009.

Graduate Research Assistant, \emph{University of Virginia}, 2005-2006.

\hypertarget{teaching}{%
\section{Teaching}\label{teaching}}

Introduction to Structural Equation Modeling, ERMA 8240, \emph{Auburn
University}, Spring 2019 -- Present.

Design and Analysis III, ERMA 8320, \emph{Auburn University}, Fall 2018.

Design and Analysis II, ERMA 7310, \emph{Auburn University}, Spring 2018
-- Present.

Design and Analysis I, ERMA 7300, \emph{Auburn University}, Spring 2017
- Fall 2018 -- Present.

Basic Methods in Education Research, ERMA 7200, \emph{Auburn
University}, Fall 2016 -- Present.

Confirmatory Factor Analysis and Scale Reliability, Statistical
Programming Workshop, University of Virginia, January, 2016.

Introduction to Multiple Imputation with the \texttt{mice} package,
Statistical Programming Workshop, University of Virginia, October, 2015.

Introduction to Multilevel Modeling, Statistical Programming Workshop,
FOCAL Lab, University of Virginia, July, 2015.

Introduction to Statistical Programming with R, Statistical Programming
Workshop, University of Virginia, Spring, 2015.

Introduction to Linear Models, University of Virginia, Curry Summer
Undergraduate Research Program, Summer 2012.

Introduction to Inferential Statistics, University of Virginia, Curry
Summer Undergraduate Research Program, Summer 2011.

Child Development, co-instructor, University of Virginia, Spring 2008.

Child Development, teaching assistant, University of Virginia,
2006-2007.

Child Development, co-instructor, Hampton Roads Center, University of
Virginia, Spring 2005.

\hypertarget{professional-activities}{%
\subsection{Professional Activities}\label{professional-activities}}

Editorial Board for \emph{Interdisciplinary Education and Psychology}.

Reviewer for \emph{Child Development}

Reviewer for \emph{Journal of Abnormal Child Psychology}

Reviewer for \emph{Early Childhood Research Quarterly}

Member, \emph{American Statistical Association }

Member, \emph{Society for Research in Child Development}

Member, \emph{American Educational Research Association}

\hypertarget{invited-workshops}{%
\subsection{Invited Workshops}\label{invited-workshops}}

SREE Workshop: Intervention Fidelity -Models, Methods, and Applications,
Fall 2014

\hypertarget{trainings-and-conferences-attended}{%
\subsection{Trainings and Conferences
Attended}\label{trainings-and-conferences-attended}}

Intensive Longitudinal Methods, Statistical Horizons, October 23-24,
2015

Mediation, Moderation, and Conditional Process Analysis, Andrew F.
Hayes, University of Virginia, June 4-5, 2015

Institute of Education Sciences Summer Research Training Institute:
Cluster-Randomized Trials, Northwestern University, July 15-26, 2012

UseR! 2012, Vanderbilt University, June 11-15, 2012

Functional MRI in Clinical Research and Practice: Measurement, Design
and Analysis, Carnegie Mellon University/University of Pittsburgh, June
13-17, 2011

Missing Data Workshop, University of Virginia, June 1-7, 2011

Society for Research in Child Development Conference, Montreal, March
31-April 3, 2011

Multi-Modal Neuroimaging Training, Martinos Medical Center, Boston,
December 13-17, 2010

Conference on Human Development, New York, April 9-12, 2010

\hypertarget{software-proficiency}{%
\subsection{Software Proficiency}\label{software-proficiency}}

R, Mplus, \LaTeX, SPSS

\hypertarget{professional-experience}{%
\section{Professional Experience}\label{professional-experience}}

Research Scientist, \emph{University of Virginia}, Charlottesville, VA,
2013-2016.

Postdoctoral Fellow, \emph{University of Virgina}, Charlottesville, VA,
2010-2013.

Team Building Coordinator, \emph{Charlottesville's Challenge Course},
Charlottesville, VA, 2002 - 2004.

Counselor/Intervention Specialist, \emph{Hoover City School System},
Hoover, AL, 1999 - 2002.

Bridges Drug Education Program Instructor, \emph{Hoover City School
System}, Hoover, AL, 1999 - 2002.

Independent Contract Work, \emph{Central Alabama}, 1997 - 2002.

Adventure Based Counselor/Case Manager, \emph{Bradford Health Services},
Pelham, AL, 1995 - 1997.

Conflict Resolution Counselor, \emph{Jemison Boy's Ranch}, Jemison, AL,
1993 - 1995.

\end{document}